HEP Software Foundation Community White Paper Working Group -- Detector Simulation

### 2018-03-02 CWP/papers/HSF-CWP-2017-07_detsim/latex/DetectorSimulation.tex
fix the HSF document number, from 13 to 7

\noindent
\begin{tabular*}{\linewidth}{lc@{\extracolsep{\fill}}r@{\extracolsep{0pt}}}
 & & HSF-CWP-2017-13 \\
 & & February 28, 2018 \\ % use \date or hardwire e.g. December 15, 2017
 & & \\
\end{tabular*}
\vspace{0.1cm}

>>>>

\noindent
\begin{tabular*}{\linewidth}{lc@{\extracolsep{\fill}}r@{\extracolsep{0pt}}}
 & & HSF-CWP-2017-07 \\
 & & February 28, 2018 \\ % use \date or hardwire e.g. December 15, 2017
 & & \\
\end{tabular*}
\vspace{0.1cm}
